Title

### 2024-05-13 paper/main.tex
Updates

\begin{abstract}
	\emph{Causal Discovery} involves learning causal structures from data,
	and has been studied both in Directed Acyclic Graphs (DAGs) and
	Structural Equation Models (SEMs). This problem has been extensively
	studied for both DAGs and SEMs. In the field of DAGs, many automated
	algorithms have been developed for constructing a DAG from a given
	dataset. However, the adaption of these algorithms in applied fields
	have been limited, possibly due to a lack of confidence in these
	algorithms stemming from them making obvious mistakes, and the
	difficulties in choosing the right algorithm for a given dataset.
	Consequently, in applied disciplines, these DAGs are predominantly
	constructed manually based on domain expertise. Due to being
	constructed by hand, it is vital that the fit of these models are
	tested against data and the models are potentially modified to acheive
	a better fit. On the other hand, in the field of SEMs models are
	typically constructed manually through an iterative process of
	assessing fit and modifying the model according to that. This process
	is commonly known as \emph{Specification Search} where methods like
	\emph{modification indices} can be used to guide this modification
	process. In the case of DAGs, although there are tests such as Shipley
	2000 that can assess the global fit of model by combining the tests
	using implied conditional independencies of the model, but there are no
	methods that can guide our modification process. In this paper, we
	present a simple modification process aimed at helping researchers in
	manually constructing or modifying the DAGs outputted by an algorithm.
	This modification process is based on using a measure of association
	for these individual local CI tests to identify the worst offending CI
	test and combining it with expert knowledge. We also present a measure
	of association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}

>>>>

\begin{abstract}
	The initial step in a causal analysis involves determining the causal
	structure between the variables from data typically in the form of a
	Directed Acyclic Graph (DAG) or an Structural Equation Model (SEM).
	This procedure, known as \emph{causal discovery}, has been extensively
	studied for both DAGs and SEMs. For DAGs, numerous automated algorithms
	have been developed that can automatically estimate the structure from
	a given dataset. However, the adaption of these algorithms in applied
	fields remain limited, possibly due to a lack of confidence in these
	algorithms stemming from them making obvious mistakes, and the
	difficulties in choosing the right algorithm for a given dataset. As a
	result, in applied disciplines, DAGs are predominantly constructed
	manually based on domain expertise which makes it vital to test the fit
	of these models to the data and potentially modifying them to improve
	the fit. On the other hand, in the field of SEMs, models are
	typically constructed manually through an iterative process of
	assessing fit and modifying the model according to that. This process
	is commonly known as \emph{specification search} where expert knowledge
	combined with methods like \emph{modification indices} can be used to 
	guide the modification process. In the case of DAGs, although
	statistical tests are available that can assess the global fit of
	model, but there are no methods that can guide our modification
	process. In this paper, we present a simple modification process aimed
	at helping researchers in manually constructing or modifying the DAGs
	outputted by an algorithm to improve its fit. This modification process
	identifies pairs of variables whose association is not fully explained
	by the model. Once such an unexplained association is found, an expert
	can start by adding edges between the worst offending pair of variables 
	while using their expertise to decide the direction between
	the variables. For the measure of association, in the case of
	continuous and discrete variables we can use effect sizes, however no
	such measure of association is present for mixed data. We propose a
	novel (conditional) measure of association for mixed data based on
	canonical correlations. We also present a graphical web-tool that can
	assist researchers in iteratively modifying and constructing their
	DAGs. We theoretically show that in the presence of an oracle, this
	iterative modification process is consistent in recovering the true
	DAG. Emprically, we show that this process performs comparably to PC
	and Hill-Climb Search algorithms if the user is able to correctly
	identify the direction of the edge in one out of three cases.
\end{abstract}
